\cvsection[page1sidebar]{Added-values}

%%%%%%%%%%%%%
%ADDED-VALUES
%%%%%%%%%%%%%

\begin{itemize}
    \item Developed customized scRNAseq pipelines for gene expression and antibody repertoire analysis using statistical models.
    \item Experienced in publishing scientific journals giving lectures and presentations at international conferences. 
    \item Collaborated in an interdisciplinary team environment to deliver project milestones on time.
    \item Highly interested in implementation of innovative technology development. 
    \item Demonstrated ability to work independently with a creative problem-solving mentality, consistently delivering high-quality results.
\end{itemize}

\cvsection[page2sidebar]{PROFESSIONAL Experiences}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Clinical Data Manager}{SGS}{Jan 2024 -- Present (6 months)}{Mechelen, Belgium}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item \small 
    Performed data cleaning and CDISC coding activities, ensuring 99\% data accuracy for a Phase III Cardiomyopathy Trial involving RNAi Therapy. 
    \item 
    Improved cleaning rule descriptions for in-house users, resulting in clarification and a 20\% reduction in data processing time.
    %\item Participated database design and user acceptance testing, achieving a 95\% approval rate from stakeholders.
    %\item Developed and implemented the CDISC SDTM coding, reducing data processing time by 20\%, in accordance with study protocols and regulatory requirements.
\end{itemize}
\smallskip

%%%%%%%%%%%%%
%Experience 2
%%%%%%%%%%%%%

\cvevent{Business Development Manager}{Cellatoz Inc.}{April 2023 -- Nov 2023 (8 months)}{Seoul, South Korea}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item \small 
    Attended BIO International Convention 2023, presented company profile to clients, and facilitated 4 successful MTAs (i.e., FujiFilm CD and Likarda), 
    resulting in a 25\% increase in collaborative projects.
    \item Sourced tonsil tissues from 2 approved donor sites in the US, ensuring 100\% donor eligibility compliance and reducing sourcing time for stem cell therapy. 
    \item Collaborated with RA team and external consultants in reviewing CMC documents for IND submission under the guidance of FDA standards and QbD principles.
    %\item Presented company profile and mission to clients, securing 3 new strategic partnerships and increasing licensing inquiries by 40\%.
    %\item Collaborated with National Cancer Center and data scientists in South Korea and protein biologists in Brussels.
    %\item Optimized and established PCR protocols for a diagnostic kit, resulting in a 30% increase in DNA yield.
    %\item Oversaw inventory management and optimized lab equipment utilization.
    %\item Supervised two MSc and four BSc students for their successful theses. numerous ethical regulations, and SOPs, and

\end{itemize}

%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%

\cvevent{Research/Teaching Assistant}{Ghent University\newline Vrije Universiteit Brussel}{Jan 2019 -- Dec 2022 (4 years)}{Brussels, Belgium}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item \small 
    Investigated vaccine development using molecular assays, leading to the discovery of key biomarkers and achieving a 25\% increase in 
    data consistency. %through optimization of experiments.
    %\item Extracted DNA/mRNA for NGS for gene expression analysis and visualization, resulting in a 30\% increase in data processing efficiency.
    %\item Designed primers and house-keeping genes for optimizing PCR protocols, resulting in a 90\% product yield. 
    %\item Attended scRNAseq workshops in UC Davis and VIB-UGent for optimizing bioinformatics pipelines, resulting in a 25\% improvement 
    \item Presented research findings at 5 regional and international conferences, effectively communicating to the scientific community.
    \item Published 2 peer-reviewed journals, received a \$50,000 grant, and supervised 2 MSc and 4 BSc students.
    \item Instructed immunology, biochemistry, and microbiology lectures and labs, leading to a 95\% student satisfaction rate.
    %including protein purification (FPLC), flow cytometry, microscopy, and tissue slides for imaging analysis.
    %\item Designed and validated prophylactic/therapeutic vaccine experiments, analyzing laboratory performance and results daily to ensure consistency and reliability.
    %\item Performed animal tissue extraction for surface and intracellular staining for phenotyping memory cells using flow cytometry,
    %\item Optimized and established PCR protocols for a diagnostic kit, resulting in a 30\% increase in test accuracy and a 25\% reduction in processing time.
    %using Seurat and Bionconductor communities for 

\end{itemize}

%%%%%%%%%%%%%3
%Experience 4
%%%%%%%%%%%%%

\cvevent{Product Engineer}{Quratis Inc.}{Jan 2018 -- Dec 2018 (12 months)}{Seoul, South Korea}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item \small
    Optimized temperature and rotator speed of bioreactors, achieving a 20\% increase in protein yield for a pilot study.
    \item Managed essential documents and key communication as a liason for the successful technology transfer of the GMP manufacturing site 
    following a site visit in Iowa.
    \item Reviewed ICH-GCP guidelines, timeline design, and Ph1 clinical protocols to ensure adherence to industry standards,
    resulting in a 15\% reduction in protocol deviations. 
    %\item Collaborated with B2B partners for GMP regulation, reducing compliance issues.
    %\item Contributed to successful GMP facility establishment in South Korea. 
    %\item Acted as a liaison between clinical and analytical teams for a Phase 2a study.
    %\item Documented product pipelines for initial public offering audit. 
    %(fermentation, purification, and lyophilization) 

\end{itemize}
\smallskip